Interactive decompositions of the life expectancy gap

### 2018-04-10 Manuscript/Abstract-DataVizDemo.Rmd
writing

```{r, echo=F, message=F, warning=F}
library(shiny) #, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #OLD version: 0.14.1, NEW: 1.0.3
library(ggplot2)#, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #OLD: 2.2.1, NEW: ggplot2_2.2.1.9000 (install dev version using devtools::install_github)
library(plotly)#, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #OLD: 4.5.6, NEW: 4.6.0
library(crosstalk)#, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #1.0.0
library(viridis)
library(scales)
library(shinythemes)
library(dplyr)
library(grid)
library(gridExtra)
library(png)
library(forcats)

@@

```{r, echo=F, message=F, warning=F}
age_decomp_results <- read.csv("../Results2/age_decomp_results.csv")

>>>>

```{r load-libraries, echo=F, message=F, warning=F}
library(shiny) #, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #OLD version: 0.14.1, NEW: 1.0.3
library(ggplot2)#, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #OLD: 2.2.1, NEW: ggplot2_2.2.1.9000 (install dev version using devtools::install_github)
library(plotly)#, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #OLD: 4.5.6, NEW: 4.6.0
library(crosstalk)#, lib.loc = "/Library/Frameworks/R.framework/Versions/3.3/Resources/library/old_versions") #1.0.0
library(viridis)
library(scales)
library(shinythemes)
library(dplyr)
library(grid)
library(gridExtra)
library(png)
library(forcats)

@@

```{r load-data, echo=F, message=F, warning=F}
age_decomp_results <- read.csv("../Results2/age_decomp_results.csv")
